---
title: "Marketing Analyitcs"
subtitle: "Homework 1"
output: pdf_document
date: "2026-03-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Product Choice

The chosen product is the Nintendo Switch 2 gaming console from TIME Best Innvoations 2025. Nintendo Switch 2 is the next generation hybrid gaming console, combining handheld and home gaming capabilities. It builds upon the success of the original Nintendo Switch ecosystem, and is launched by one of the key market player, Nintedo, which comprises 27% of the market [1].

## Product for Look-alike analysis

The product I have chosen for the analysis is the Play Station Portable (PSP) by Sony. It is a similar handheld gaming console also small and portable like the Nintendo Switch. Both products target the same gaming audience, so the behavior of sales of the new product in the markett will be much alike with the behavior of the old one, and the shape of the curve will be similar. Both products rely heavily on ecosystem development and social contagion. They are functionally very similar and can be viewed as old and new versions of the same technology. The PSP introduced console-level graphics in a handheld format, multimedia capabilities (music, video playback), and online connectivity — features that were advanced for its time. Similarly, the Nintendo Switch 2 builds upon portable gaming by offering hybrid functionality (handheld + docked mode), improved GPU performance, and integration with Nintendo’s digital ecosystem.

Moreover, PSP is already quite old and can be considered as a product that has already finished its lifecycle. So, we can see the whole S-shaped curve in its sales graph. This will help us create an accurate graph for Nintendo Switch 2. This is the reason I have chosen PSP and not Nintendo Switch 1 since it is not old enough and is still in the maturity stage, and we cannot see the decline.

## Data

I have used a dataset from Statista, summarizing PSP unit sales fromm 2004 until 2022 [2].

```{r}
source("../helper_functions.R")
libs <- c("ggplot2","ggpubr","diffusion", "readxl")

new_libs <- libs[!(libs %in% installed.packages()[,"Package"])]
if(length(new_libs)>0) install.packages(new_libs)

lapply(libs, library, character.only = TRUE)
```
```{r}
# PSP yearly sales (million units)
data <- read_excel(
  "../data/Data.xlsx",
  sheet = "Data",
  range = "B5:C16"
)
names(data) <- c("Year", "Sales")

psp_sales <- data$Sales
t_psp <- 1:length(psp_sales)
```

I am using the diffusion library for estimating the parameters p, q, and m for PSP diffuaion.
```{r}
psp_model <- diffusion(psp_sales)

p_psp <- psp_model$w["p"]
q_psp <- psp_model$w["q"]
m_psp <- psp_model$w["m"]

p_psp
q_psp
m_psp
```
P is the coefficient of innovation and is estimated to be 0.036, meaning that there is 3.6% probability of adoption from external factors (e.g., advertising, marketing campaigns) independent of whether others have adopted the product. Q is 0.574 meaning that there is 57.4% probability of adoption from internal factors (e.g., word-of-mouth, network effects) based on the number of previous adopters. These are the immitators. We can say that these values are quite realistic since we can also see from real-world experience that there is a small percent of people who would try a new gaming console immediately. These are the gaming fans that want to be the first to try the product. And there is a high percent of people who will listen to feedbacks and get influenced to also buy the product.


Using the Bass function we predict the PSP sales to see whether they match the actual data.
```{r}
psp_pred <- bass_f(t_psp, p_psp, q_psp) * m_psp

psp_df <- data.frame(
  Year = 2004:2014,
  Sales = psp_sales,
  Predicted = psp_pred
)

ggplot(psp_df, aes(x=Year, y=Sales)) +
  geom_bar(stat="identity") +
  geom_point(aes(y=Predicted), color="red", size=3) +
  ggtitle("PSP Sales: Actual vs Bass Model Prediction") +
  ylab("Million Units")
```
As seen on the graph, the predictions follow the same path as the data.

```{r}
ggplot(data.frame(t=c(0,10)), aes(x=t)) +
  stat_function(
    fun=function(x) bass_f(x, p_psp, q_psp)
  ) +
  ggtitle("PSP Adoption Curve")
```

To conduct the Look-alike analysis, we take the same p and q as in the PSP Bass model. We estimate the market potential using the fact that Nintendo Switch 1 has had 155 million sales (worldwide) by 2026 since launch 9 years before [3]. We can say that the second Nintendo will have around the same market potential, so we can take the 160 million for the first 11 years. This way we will get the estimation of worldwide sales till 2035. 

Since Nintendo Switch 2 is a product of worldwide interest and gamers across the world are interested in it, it is more useful to predict the worldwide sales.
```{r}
p_sw2 <- p_psp
q_sw2 <- q_psp
m_sw2 <- 160

t_sw2 <- 1:11

# Cumulative adoption
sw2_cumulative <- bass_F(t_sw2, p_sw2, q_sw2) * m_sw2

# Annual sales (discrete difference)
sw2_adoption <- c(sw2_cumulative[1],
                  diff(sw2_cumulative))

sw2_df <- data.frame(
  Year = 2025:2035,
  Sales = sw2_adoption,
  Cumulative_Sales = sw2_cumulative
)

```

```{r} 
ggplot(sw2_df, aes(x=Year, y=Sales)) +
  geom_bar(stat="identity") +
  ggtitle("Nintendo Switch 2 Predicted Annual Adoption") +
  ylab("Million Units")
```
```{r}
ggplot(sw2_df, aes(x=Year, y=Cumulative_Sales)) +
  geom_line(size=1.2) +
  ggtitle("Nintendo Switch 2 Cumulative Adoption (Bass Model)") +
  ylab("Million Units")
```
The table shows the yearly sales as well as cumulative sales prediction of Nintendo Switch 2. 
```{r}
print(sw2_df)
```

## References
[1] Statista. (2025). Game consoles market revenue worldwide. Statista Market Insights. https://www.statista.com/outlook/cmo/consumer-electronics/gaming-equipment/game-consoles/worldwide

[2] Statista. (2025, July 10). Sony PlayStation Portable and PlayStation Vita unit sales worldwide from 2004 to 2022.  https://www.statista.com/statistics/1029044/worldwide-sony-playstation-vita-unit-sales

[3] Towey, H. (2026, February 3). Nintendo Switch becomes the company’s best-selling console ever. CNBC. https://www.cnbc.com/2026/02/03/nintendo-switch-best-selling-console-gaming.html




